Distributional Trees and Forests

### 2017-06-23 pkg/disttree/inst/useR2017/slides.Rnw
added new data for 'simlist'
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@1482 255f4249-2263-4417-b1ea-8498779e27a7

<<get_simlist, echo=FALSE, results=hide>>=
if(file.exists("simlist.rda")){
  load("simlist.rda")
} else {
  source("gensimlist.R")
  simlist <- gensimlist(seed = 7, nrep = 100, ntree = 100)
  save(simlist, file = "simlist.rda")
}

>>>>

<<get_simlist, echo=FALSE, results=hide>>=
if(file.exists("simlist.rda")){
  load("simlist.rda")
} else {
  source("gensimlist.R")
  simlist <- gensimlist(seed = 9, nrep = 150, ntree = 100)
  save(simlist, file = "simlist.rda")
}
